Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-02-06 paper/arxiv-submission/main.tex
resolve Float too large for page resolve ""
fix "Command \r invalid in math mode"

@@

    % Figure 3: Limiting Potential Volcano Plot and Periodic Table
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=\textwidth]{main_fig3_volcano.png}
        \caption{\textbf{Limiting potential volcano plot and periodic table.}
        \textbf{a}. Limiting potential volcano plot computed from hybrid-descriptor-based
        linear scaling relations at potential of -0.17 V vs SHE.
        In the plot, the circle, triangle, square, diamond, plus, and star symbols represent
        metals supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene,
        graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N, respectively.
        Dotted purple lines delineate regions representing rate-determining steps,
        with roman numerals denoting the respective RDS for each region.
        The reaction steps are defined in \cref{main_eq1:co2rr1} to \cref{main_eq8:co2rr8}.
        \textbf{b}. Limiting potential periodic table illustrating the theoretical activity of
        single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.}
        \label{main_fig3:volcano}
    \end{figure}

@@

    \subsection{DFT calculations}
    Spin-polarized density functional theory calculations were performed using the Vienna Ab initio Simulation Package (VASP) version 5.4.4 \cite{kresse1996efficient, kresse1996efficiency, kresse1993ab} to optimize geometries and determine the electronic structure.
    The Perdew-Burke-Ernzerhof (PBE) functional \cite{kresse1996efficient} within the generalized gradient approximation (GGA) \cite{perdew1996generalized} was utilized to describe the electron-ion interactions and electronic exchange correlations.
    Kohn-Shan equations were approached employing a plane-wave basis set with a cut-off energy of 440 eV.
    Geometry optimizations were performed using $\Gamma$-Centered K-point meshes of ($2\times2\times1$) until the force on each atom fell below 0.02 eV/\(\mathrm{\AA}^{-1}\).
    Electronic structure calculations utilized denser K-point meshes of ($3\times3\times1$) and employed self-consistent field (SCF) methods.

>>>>

\DeclareSIUnit\angstrom{\text {Å}}

@@

    % Figure 3: Limiting Potential Volcano Plot and Periodic Table
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.9\textwidth]{main_fig3_volcano.png}
        \caption{\textbf{Limiting potential volcano plot and periodic table.}
        \textbf{a}. Limiting potential volcano plot computed from hybrid-descriptor-based
        linear scaling relations at potential of -0.17 V vs SHE.
        In the plot, the circle, triangle, square, diamond, plus, and star symbols represent
        metals supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene,
        graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N, respectively.
        Dotted purple lines delineate regions representing rate-determining steps,
        with roman numerals denoting the respective RDS for each region.
        The reaction steps are defined in \cref{main_eq1:co2rr1} to \cref{main_eq8:co2rr8}.
        \textbf{b}. Limiting potential periodic table illustrating the theoretical activity of
        single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.}
        \label{main_fig3:volcano}
    \end{figure}

@@

    \subsection{DFT calculations}
    Spin-polarized density functional theory calculations were performed using the Vienna Ab initio Simulation Package (VASP) version 5.4.4 \cite{kresse1996efficient, kresse1996efficiency, kresse1993ab} to optimize geometries and determine the electronic structure.
    The Perdew-Burke-Ernzerhof (PBE) functional \cite{kresse1996efficient} within the generalized gradient approximation (GGA) \cite{perdew1996generalized} was utilized to describe the electron-ion interactions and electronic exchange correlations.
    Kohn-Shan equations were approached employing a plane-wave basis set with a cut-off energy of 440 eV.
    Geometry optimizations were performed using $\Gamma$-Centered K-point meshes of ($2\times2\times1$) until the force on each atom fell below \SI{0.02}{\electronvolt\per\angstrom}.
    Electronic structure calculations utilized denser K-point meshes of ($3\times3\times1$) and employed self-consistent field (SCF) methods.
